\subsection{Arithmetic with fractions 分数的四则运算}

\paragraph{Addition and subtraction 加减法} \ \ \\

\begin{paracol}{2}
Two fractions may be added or subtracted as follows:
\begin{enumerate}
\item Write each fraction using a common denominator
\item Add or subtract the numerators and keep the same denominator
\item Simplify the fractions if needed
\end{enumerate}
\switchcolumn[1]
分数的加减法如下：\\ 
\begin{enumerate}
\item 通分，将两个数写成分母相同的形式；
\item 分子相加或者相减；\\ 
\item 如果需要约分的就约分。
\end{enumerate}
\end{paracol}

\begin{example}
$\dfrac{1}{4} + \dfrac{5}{6}$
\end{example}
\begin{solution}
Method 1: Use the product of the two denominators as a common denominator. 方法一：利用两个分母的乘积作为共同的分母。
$$
\dfrac{1}{4} + \dfrac{5}{6} = \dfrac{1\times 6}{4\times 6} + \dfrac{5\times 4}{6\times 4} = \dfrac{6}{24} + \dfrac{20}{24} = \dfrac{26}{24} = \dfrac{13}{12}.
$$

Method2: Use the LCM of the denominators as a common denominator. This method is preferred to Method 1 as, in general, the final solution is further reduced than the solution using Method 1. 方法二：用两个分母的最小公倍数作为分母。相比于前一种方法，这样可以减少一些约分简化的过程。
$$
\dfrac{1}{4} + \dfrac{5}{6} = \dfrac{1\times 3}{4\times3} + \dfrac{5\times 2}{6\times 2} = \dfrac{3}{12} + \dfrac{10}{12} = \dfrac{13}{12}.
$$


\end{solution}

\begin{example}
$
\dfrac{5}{6} - \dfrac{3}{4}
$
\end{example}
\begin{solution}
$$
\dfrac{5}{6} - \dfrac{3}{4} = \dfrac{10}{12} - \dfrac{9}{12} = \dfrac{1}{12}.
$$
\end{solution}

\paragraph{Multiplication 乘法} \ \ \\

\begin{paracol}{2}
To multiply two fractions we simply multiply their numerators and multiply their denominators, reducing the answer if possible. To multiply an integer by a fraction, first write the integer as a fraction and then multiply as usual. Or simply multiply the integer with the numerator. 
\switchcolumn[1]
分数乘分数,用分子相乘的积做分子，分母相乘的积做分母,能约分的要约成最简分数。分数乘整数时，用分数的分子和整数相乘的积做分子，分母不变。（要约成最简分数）
\end{paracol}

\begin{example}
$\dfrac{2}{3}\times \dfrac{3}{4}$
\end{example}
\begin{solution}
$$
\dfrac{2}{3}\times \dfrac{3}{4} = \dfrac{2\times 3}{3\times 4} = \dfrac{6}{12} = \dfrac{1}{2}.
$$
Effectively the answer is reduced to lowest terms during multiplication. 我们也可以在乘的时候约分。
$$
\dfrac{2}{3}\times \dfrac{3}{4} = \dfrac{{\color{blue}\bcancel{2}}^1}{{\color{red}\bcancel{3}}^1}\times \dfrac{{\color{red}\bcancel{3}}^1}{{\color{blue}\bcancel{4}}^2} = \dfrac{1\times 1}{1\times 2} = \dfrac{1}{2}.
$$

\end{solution}

\paragraph{Division 除法} \ \ \\

\begin{paracol}{2}
To divide a fraction by a whole number, you may either divide the numerator by the number, if it goes evenly into the numerator, or multiply the denominator by the number. To divide a number by a fraction, multiply that number by the reciprocal of that fraction.
\switchcolumn[1]
如果是分数除以一个整数，我们可以用分子除以这个数作为分子，也可以用分母乘以这个数做分母。如果是分数除以一个分数等于被除数乘以除数的的倒数。
\end{paracol}

\begin{example}
$\dfrac{10}{3}\div 5$
\end{example}
\begin{solution}
$$\dfrac{10}{3}\div 5 = \dfrac{10\div 5}{3} = \dfrac{2}{3}.$$
Or 或者
$$\dfrac{10}{3}\div 5 = \dfrac{10}{3\times5} =\dfrac{10}{15} = \dfrac{2}{3}.$$
\end{solution}

\begin{example}
$\dfrac{1}{2}\div \dfrac{3}{4}$
\end{example}
\begin{solution}
$$\dfrac{1}{2}\div \dfrac{3}{4}= \dfrac{1}{2}\times \dfrac{4}{3} = \dfrac{1\times 4}{2\times 3} = \dfrac{2}{3}.$$
\end{solution}
   \newpage