\subsection{Arithmetic with decimals 小数的四则运算}

\paragraph{Addition 加法} \ \ \\

\begin{paracol}{2}
We assume that you are familiar with the decimal number system and arithmetical operations on integers (whole numbers). Two decimal numbers may be added as follows:
\begin{enumerate}
\item The numbers are written one below the other with the decimal points vertically aligned
\item The numbers are added as if they are whole numbers
\item A decimal point is placed in the sum such that it is directly below the decimal points in the numbers being added
\end{enumerate}
\switchcolumn[1]
小数的加法和整数的加法类似，小数加法的竖式有以下的要点：\\ \\ 
\begin{enumerate}
\item 列竖式时小数点要对齐；\\ \\ 
\item 和整数的加法一样，从最低位加起，满十向前一位进一；
\item 添加和的小数点，和的小数点和加项对齐。
\end{enumerate}
\end{paracol}

\begin{example}
123.45+37.50
\end{example}
\begin{solution}

$$
\begin{array}{lcccccc}
&&1&&&&\\
&1&2&3&.&4&5\\
+&&3&7&.&5&\\
\hline
&1&6&0&.&9&5
\end{array}
$$
$123.45+37.50 = 160.95$.
\end{solution}

\paragraph{Subtraction 减法} \ \ \\

\begin{paracol}{2}
Subtracting one decimal from the other is similar to addition. Two positive decimal numbers may be subtracted as follows:
\begin{enumerate}
\item The numbers are written one below the other with the decimal points vertically aligned
\item Mentally place a zero in any places where only one of the numbers has a digit.
\item The numbers are subtracted as if they are whole numbers
\item A decimal point is placed in the sum such that it is directly below the decimal points in the numbers being subtracted
\end{enumerate}
\switchcolumn[1]
小数的减法和整数的减法类似，小数减法的竖式有以下的要点：\\ 
\begin{enumerate}
\item 列竖式时小数点要对齐；\\ \\ 
\item 如果竖式中只有一个数假设另一个数位零；
\item 和整数的减法一样，从最低位减起，不够减借一还十；
\item 添加结果的小数点，小数点和减项对齐。
\end{enumerate}
\end{paracol}

\begin{example}
123.4-37.45
\end{example}
\begin{solution}
$$
\begin{array}{lcccccc}
&0&11&12&.&13&\\
&0&\bcancel{1}&\bcancel{2}&.&\bcancel{3}&10\\
&\bcancel{1}&\bcancel{2}&\bcancel{3}&.&\bcancel{4}&{\color{green} \bcancel{0}}\\
-&&3&7&.&4&5\\
\hline
&&8&5&.&9&5
\end{array}
$$
$123.4-37.45 = 85.95$.
\end{solution}

\paragraph{Multiplication 乘法} \ \ \\

\begin{paracol}{2}
Two decimal numbers may be multiplied as follows:
\begin{enumerate}
\item The numbers are are written one below the other with the rightmost digit aligned.
\item Starting on the right, multiply each digit in the top number by each digit in the bottom number, just as with whole numbers (ignore the decimal points).
\item Add the products.
\item Place the decimal point in the answer by starting at the right and moving a number of places equal to the sum of the decimal places in both numbers multiplied.
\end{enumerate}
\switchcolumn[1]
小数乘法的竖式有以下的要点：\\  
\begin{enumerate}
\item 列竖式时数字靠右对齐；\\ 
\item 忽略小数点，从乘数的最低位起，乘以被乘数；\\ \\ 
\item 把所有乘得的结果相加；
\item 看因数中一共有几位小数，就从积的右边数几位点上小数点。
\end{enumerate}
\end{paracol}

\begin{example}
$23.45\times 2.3$
\end{example}
\begin{solution}
$$
\begin{array}{lcccc}
&2&3.&4&5\\
\times&&&2.&3\\
\hline
&7&0&3&5\\
4&6&9&0&\\ \hline
5&3.&9&3&5
\end{array}
$$
$23.45\times 2.3= 53.935$.
\end{solution}

\paragraph{Division 除法} \ \ \\

\begin{paracol}{2}
The way to do the division by a decimal number is as follows:
\begin{enumerate}
\item Convert the divisor to a whole number first if it is not by multiplying both numbers by 10, 100, etc. .
\item Ignore the decimal point of the dividend; use Long Division as with whole numbers. If there is remainder, add 0 and continue to do the division until certain accurarcy.
\item Put the decimal point upon the answer above in the same spot as the dividend (number being divided).
\end{enumerate}
\switchcolumn[1]
小数除法的竖式的方法如下：\\  
\begin{enumerate}
\item 列竖式时小数点要对齐；\\ \\ 
\item 忽略被除数的小数点，按照整数的除法计算。如果除到被除数的末尾有余数，就在余数后面添0再继续除；\\ 
\item 商的小数点和被除数的小数点对齐。
\end{enumerate}
\end{paracol}

\begin{example}
Perform the following division without using a calculator, rounding to 2 decimal places:
$$1.27\div 0.7$$
\end{example}
%\multicolumn{3}{c}{\fcolorbox{black}{black}{\color{white}\ \ \ Step 1\ \ \ }}\\
\begin{solution}
$$1.27\div 0.7 = 12.7 \div 7$$
$$
\arraycolsep=0pt
\begin{array}{rccccc}
&&\quad 1.\quad&\quad8\quad&\quad 1\quad&\quad4\\
\cline{2-6}
7&{\Big)}\ \ 1\quad&\quad2.\quad&\quad7\quad&&\\
&&\quad7\quad&\quad\downarrow\quad&&\\
\hline
&&\quad5\quad&\quad7\quad&&\\
&&\quad 5\quad&\quad 6\quad&&\\ \hline
&&&\quad 1\quad&\quad 0\quad&\\
&&&&\quad 7\quad&\\ \hline
&&&&\quad 3 \quad&\quad 0\\
&&&&\quad 2 \quad&\quad 8\\ \hline
&&&&&\quad 2
\end{array}
$$
$12.7\div 0.7 \approx  1.81$.
\end{solution}

   \newpage