\subsection{Comparing and ordering 小数和分数的比较}
\begin{paracol}{2}
The method to compare decimals is as follows.
\switchcolumn[1]
比较两个小数的方法如下：
\end{paracol}

\begin{newalg}[Comparison of decimals 小数的比较方法]
\begin{enumerate}
\item {\bf Compare the whole numbers to the left of the decimal point.} If they are not the same, the smaller decimal number is the one with the smaller whole number.
\item {\bf Compare the whole number to the right of the decimal point.} Starting from the digit on the right of the decimal point, compare the digits. The smaller digit number is the one with the smaller whole number.
\end{enumerate}

\begin{enumerate}
\item {\bf 比较整数部分。如果整数部分不同，则整数部分小的数小。} 
\item  {\bf 比较小数部分。如果整数部分相同，再比较小数部分。小数部分第一位大的那个数就大；如果第一位上的数相同，就比较第二位上的数……依次比下去。} 
\end{enumerate}
\end{newalg}


\begin{paracol}{2}
Comparing fractions with the same denominator yields the same result as comparing the numerators. One way to compare fractions with different numerators and denominators is to find a common denominator. If two positive fractions have the same numerator, then the fraction with the smaller denominator is the larger number.
\switchcolumn[1]
如果分数的分子相同，则只需要比较两个分数的分子，分子大的分数比较大。所以分数通常的比较方法是先通分，使得两个分数的分母相同，然后比较分子。另外，如果分数的分子相同，则分母大的分数比较小。
\end{paracol}

\begin{example}
Compare these numbers 比较下面的数字
$$
\begin{matrix}
a) 2.9, \ \  3.11\quad & b)  6.51,\ \ 6.38  & c)  2.7\ \ 2.70 & d) \dfrac{6}{11}, \ \ \dfrac{8}{11} & e) \dfrac{6}{5}, \ \ \dfrac{8}{7} 
\end{matrix}
$$
\end{example}
\begin{solution}

{
\centering
\begin{tabular}{|c|p{10cm}|}
\toprule	
& \parbox[c]{10cm}{\centering Why? 原因}\\
\midrule
${\color{red}2}.9 < {\color{red}3}.11$ & The numbers to the left of the decimal point of the first number is smaller. 第一个数的整数部分小\\ \hline
$6.{\color{red}5}1 > 6.{\color{red}3}8$ & The tenth of the first number is greater.  第一个数十分位大\\ \hline
${\color{red}2.7} = {\color{red}2.70}$& All place value are the same.  两个数各位都相同。\\ \hline
$\dfrac{\color{red} 6}{11}<\dfrac{\color{red} 8}{11}$ & The denominators are the same and the numerator of the first number is smaller. 分母相同，第一个数的分子较小\\ \hline
$\dfrac{6}{5} > \dfrac{8}{7}$ & $\dfrac{6}{5} = \dfrac{\color{red} 42}{35} > \dfrac{8}{7} = \dfrac{\color{red} 40}{35}$ \\ 
\bottomrule
\end{tabular}
}

\end{solution}

\begin{exercise}
\begin{paracol}{2}
\begin{enumerate}
\item 1
\item 2
\item 3
\item 4
\end{enumerate}
\switchcolumn[1]
\begin{enumerate}
\item 1
\item 2
\item 3
\item 4
\end{enumerate}
\end{paracol}
\end{exercise}
   \newpage