\subsection{Mixed calculation 加减混合运算}

\paragraph{Changing the order of operations  改变运算顺序}
\ \  

\begin{paracol}{2}
Sometimes, it is convinient to change the order of operations in the mixed equation with only addition and subtraction.
\switchcolumn[1]
在只有加减运算的算式中，有时改变加、减的运算顺序可使计算显得十分巧妙！
\end{paracol}

\begin{example}
$10-9+8-7+6-5+4-3+2-1$
\end{example}
\begin{solution}
\begin{paracol}{2}
If this question is added or subtracted in order from left to right, it is possible to draw a correct result. However,  it is more complicated  and easier to make a mistake. If you change the order of the operations, doing the subtraction first, the computation will be easier. The formula in parentheses indicates  calculating first.
\switchcolumn[1]
这题如果从左到右按顺序进行加减运算，是能够得出
正确结果的。但因为算式较长，多次加减又繁又慢且容易
出错。如果改变一下运算顺序，先减后加，就使运算显得
非常“漂亮”。下式括号中的算式表示先算。
\end{paracol}
$$
\begin{aligned}
&10-9+8-7+6-5+4-3+2-1\\
=&(10-9)+(8-7)+(6-5)+(4-3)+(2-1)\\
=&1+1+1+1+1 = 5.\\
\end{aligned}
$$

\end{solution}

\paragraph{Changing the order of terms with the sign  带着“+”、“-”号搬家}
\ \  

\begin{example}
$1-2+3-4+5-6+7-8+9-10+11$
\end{example}
\begin{solution}
\begin{paracol}{2}
How to compute $1-2$? To make it simple. We can move $+3$ to the front of $-2$. And similarly we can move $+5$ to the front of $-4$. We can simplify the computation with this technique. When you move the terms, just remember move with the sign.
\switchcolumn[1]
这题只有加减运算，而且1-2不够减。我们可以采用
带着加减号搬家的方法解决。要注意每个数自己的符号就
是这个数前面的那个“+”号或“-”号，搬家时要带着符
号一起搬。，把“+3”搬到“-2”的前面，把
“+5” 搬到了“-4” 的前面， …… 把“+11” 搬到了
“-10”的前面，这就叫带着符号搬家。巧妙利用这种搬
法，可以使计算简便。
\end{paracol}
$$
\begin{aligned}
&1-2+3-4+5-6+7-8+9-10+11\\
=&1+3-2+5-4+7-6+9-8+11-10\\
=&1+(3-2)+(5-4)+(7-6)+(9-8)+(11-10)\\
=&1+1+1+1+1+1=6
\end{aligned}
$$
\end{solution}
   \newpage