\subsection{Basic concept of statistics 统计基础知识}
\begin{paracol}{2}
Statistics is a branch of mathematics dealing with the collection, analysis, interpretation, presentation, and organization of data. "Data" usually refer to a specific group of numbers. Sometimes, data can also refer to information as a general concept rather than to specific collections of numbers. One way to provide information about a list of numbers is to use a single number to describe some feature of the numbers in the list. Here are some basic ways to choose that representative value.
\switchcolumn[1]
统计学是一种科学的数学分支，是关于收集、分析、解释、陈述数据的科学。数据通常指的是某一组数字，有时我们也用数据这个词指一个整体的概念。一种体现一组数据的特点的方式是找到一个数字来表达。下面就是几个特殊的表达：
\switchcolumn[0]*
\begin{itemize}
\item {\bf Average: } The average of a group of numbers is the sum of the numbers divided by the number of numbers in the group. The average is also called the mean or the arithmetic mean.
\item {\bf Median: } The median is the value separating the higher half of a group of numers from the lower half. The median of a finite list of numbers can be found by arranging all the numbers from smallest to greatest. If there is an odd number of numbers, the middle one is picked. If there is an even number of observations, the median is then usually defined to be the mean of the two middle values.
\item {\bf Mode: } The mode of a set of data values is the value that appears most often.
\end{itemize}
\switchcolumn[1]
\begin{itemize}
\item {\bf 平均数：} 平均数是一组数的和除以这组数的数量。平均数又可成为算术平均数或均值。\\ \\ 
\item {\bf 中位数：} 中位数是可将一组数划分为相等的上下两部分。对于有限的数集，可以通过把所有观察值高低排序后找出正中间的一个作为中位数。如果观察值有偶数个，通常取最中间的两个数值的平均数作为中位数。\\ \\ \\ \\ 
\item {\bf 众数：} 众数指一组数中出现次数最多的数值。
\end{itemize}
\end{paracol}


\begin{example}
Suppose the following are your grades on tests: 下面是你多次考试得到的成绩：
$$
70, 84, 91, 100, 96, 94, 60, 80, 96, 97
$$
\begin{enumerate}
\item What is the average of your test scores? 平均成绩是多少分？
\item What is the median of your test scores? 成绩的中位数是多少？
\item What is the mode of your test scores? 成绩的众数是多少？
\end{enumerate}
\end{example}
\begin{solution}
1. To find the average, we divide the sum of the scores y the number of scores: 计算平均值，用所有分数的和除以成绩的个数。
$$
\dfrac{70+84+91+100+96+94+60+80+96+97}{10} = \dfrac{868}{10} = 86.8
$$
2. We list the grades in order: 首先我们把所有分数排序：
$$
60, 70, 80, 84, 91, 94, 96, 96, 97, 100.
$$
The median is  所以中位数为：
$$\dfrac{91+94}{2} = 92.5.$$
3. The grade $96$ occurs twice, and other grade only occurs once. Therefore, $96$ is the mode. 分数$96$出现了两次，而其他的分数只出现了一次，所以众数为$96$。
\end{solution}
\newpage
